A star formation event in the leading arm of the Magellanic stream triggered by passage through the outer Galactic disk

### 2018-11-01 ms.tex
move figure

\todo{Make a PGM for this model?}

We also use the posterior samples from the hierarchical inference to compute the posterior probabilities that each source is a member of the cluster.
\figurename~\ref{fig:hierarch-iso} shows the \decam\ photometry for all sources with membership probability $> 0.5$ (circle markers).
Over-plotted (blue, solid lines) are \acronym{MIST} isochrones computed from 128 randomly chosen posterior samples, shifted to the distance of the given sample and extincted given the $A_V$ value of the sample.
Also plotted is the equal-mass binary sequence (green, dashed line) computed from the median posterior sample, highlighting that the cluster may contain an abundance of binary star systems.

@@

\todo{APW}

@@

\subsection{Relation to \hi gas}
\label{sec:higas}

>>>>

% TODO: Make a PGM for this model?

@@

We also use the posterior samples from the hierarchical inference to compute the posterior probabilities that each source is a member of the cluster.
\figurename~\ref{fig:hierarch-iso} shows the \decam\ photometry for all sources with membership probability $> 0.5$ (circle markers).
From the stellar population modeling described above (\sectionname~\ref{sec:popmodel}), we find that \clustername\ is indeed young, distant, and metal poor, with median posterior values of age $\tau \approx 130~\textrm{Myr}$, distance $D \approx 29~\kpc$, and metallicity $\feh \approx -1.1$.
Over-plotted in \figurename~\ref{fig:hierarch-iso} (blue, solid line) is a \acronym{MIST} isochrone with these parameters, shifted to the median distance and extincted given the median $A_V$ value.
Also plotted is the equal-mass binary sequence (green, dashed line) computed from the median posterior sample, highlighting that the cluster may contain an abundance of binary star systems.

@@

\subsection{Relation to the Magellanic stream}
\label{sec:higas}
